---
title: "Review 1 Part 2"
output: pdf_document
date: "2025-09-17"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Instructions

This is the second part of your review. You are allowed to use all the materials listed as part of the overall review instructions.

In the case that you have trouble compiling the PDF file, please submit the RMD file. For problems that have multiple parts, I will award partial credit where appropriate.

(**Note:** If you have trouble seeing equations, make sure you use the visual mode or cross reference the PDF).

Before you start, run the following code chunk to set everything up:

```{r, message=FALSE}
library(tidyverse)
if (!require(DescTools)) {
  install.packages("DescTools")
}
set.seed(105)
```

**Your name**:

\newpage

# Law of Large Numbers

In class, we talked about the law of large numbers and the properties of the sample mean. In this section, let's perform some simulations to verify the identities we saw in class numerically.

## Question 1

Suppose $X \sim BIN(40, 0.7)$, which is a binomial distribution. Sample 100 numbers from the distribution and call it `x`.

```{r}
## Your code here

```

## Question 2

Find the sample mean and standard deviation of `x`.

```{r}
## Your code here

```

## Question 3

Are the values you found in Question 2 close to what you expect? Make sure you mention the exact values from the distribution.

**Your answer**:

## Question 4

Now, find the mean for `x`, but for samples sizes of 5, 50, and 500. (You need to sample again. You can do these three steps separately, but you are welcomed to use a `for` loop if you are comfortable with it. Also, the sample size refers to how many you sample, not the parameter of the binomial distribution.)

```{r}
## Your code here

```

## Question 5

Is the sample mean more accurate when you increase the sample size? Explain using the actual values you found in Question 4.

**Your answer**:

## Question 6

Now, you remembered that we also learned about the median. Find the population median from the distribution using the Inverse CDF, not your samples. (Hint: Remember the quantile of the median).

```{r}
## Your code here

```

## Question 7

Is the median you found in **Question 6** close to the mean of the distribution? What does this say about the shape of the distribution?

**Your answer**:

\newpage

# Real Data Analysis

Consider the food access dataset again. This time, the dataset has been preprocessed with only census tracts from Texas and a random sample has been taken. This dataset is named as `review2_data.csv` in the Review 2 folder. The corresponding data dictionary is included as well.

Note: Don't use the previous full dataset we used in class because you will get different results.

## Question 8

Load the dataset into R and name it `food`. (Remember to put the dataset in the same folder as your R Markdown file and double check the name of the file for an exact match.)

```{r}
## Your code here

```

## Question 9

Notice that the column `LILATracts_Vehicle` is binary, which means that this is a proportion problem. In this case, find a 99% confidence interval for the proportion.

```{r}
## Your code here

```

## Question 10

Write a conclusion for Question 9. Make sure you include the context of the problem about the parameter rather than using generic languages.

**Your answer**:

## Question 11

Suppose that you are interested in the average Occupied Housing Units (`OHU2010`) per census tract. Find a 99% confidence interval using R.

```{r}
## Your code here

```

## Question 12

Write a conclusion for Question 11. Make sure you include the context of the problem about the parameter rather than using generic languages.

**Your answer**:
